\textsf{Are large language models superhuman chemists?}

### 2024-03-26 src/tex/ms.tex
radarplot opacity
update dependencies for end-to-end-run

% Calculation vs. no calculation
Given that some of the questions in \chembench require elaborate calculations, we also analyzed if the models perform differently on those questions.
For this, we manually annotated the questions that require calculations and performed the analysis on only those questions.  % TODO add some analysis here

@@

\subparagraph{Number of NMR peaks} 
To generate the \variable{output/question_count_per_dir/json_file_counts_name_to_smiles.txt}  tasks about the number of \gls{nmr} peaks, we randomly sampled \gls{smiles} from the ZINC database\autocite{Irwin_2012} and then used OpenChemLib\autocite{openchemlib} to compute the number of diasterotopically distinct hydrogen atoms. 
We then sampled from the set of number of peaks (excluding the correct answer) to obtain the false answer options.

>>>>

% % Calculation vs. no calculation
% Given that some of the questions in \chembench require elaborate calculations, we also analyzed if the models perform differently on those questions.
% For this, we manually annotated the questions that require calculations and performed the analysis on only those questions.  % TODO add some analysis here

@@

\subparagraph{Number of NMR peaks} 
To generate the \variable{output/question_count_per_dir/json_file_counts_number_of_nmr_peaks.txt}  tasks about the number of \gls{nmr} peaks, we randomly sampled \gls{smiles} from the ZINC database\autocite{Irwin_2012} and then used OpenChemLib\autocite{openchemlib} to compute the number of diasterotopically distinct hydrogen atoms. 
We then sampled from the set of number of peaks (excluding the correct answer) to obtain the false answer options.
